### 2020-07-18 article.tex
A bit longer description of SLEPc

With these added functions, it is now possible to do code refactorization for
applications that deal with multiple right-hand sides.  As a striking example,
LOBPCG~\cite{knyazev2001toward} or CISS~\cite{sakurai2003projection}
implementations in SLEPc~\cite{hernandez2005ssf}, the Scalable Library for
Eigenvalue Problem computations built on top of PETSc, were previously not
using blocking when applying the preconditioner or solving linear systems. This has been rewritten for version 3.14.0 and the benefit of
this new implementation is displayed in~\cref{sec:lobpcg}.

>>>>

With these added functions, it is now possible to do code refactorization for
applications that deal with multiple right-hand sides. This is the case of some
eigensolvers in SLEPc~\cite{hernandez2005ssf}, the Scalable Library for
Eigenvalue Problem computations. SLEPc is an add-on library that extends PETSc
with several classes for linear and nonlinear eigenvalue problems, as well as
tools to, e.g., facilitate the use of shift-and-invert spectral transformations.
The implementations of LOBPCG~\cite{knyazev2001toward} and CISS~\cite{sakurai2003projection}
in SLEPc were previously not using blocking when applying the preconditioner or solving linear systems.
In version 3.14.0 we have adapted these solvers to employ \pk{KSPMatSolve} and \pk{PCMatApply}.
In the case of LOBPCG, which is a purely blocked method, all steps were already
implemented as block operations, except the applications of the preconditioner,
which ruined the benefits of blocking. With the new implementation, the gains
are striking, as reported in~\cref{sec:lobpcg}.
